{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-10-12 paper/tex/sections/variations.tex
minor changes to variations

In models \modBetaLow{}-\modBetaHigh{}, we set the mass transfer efficiency $\beta$ to a fixed value. For the BHBHs and BHNSs, as we increase $\beta$ the detection rates steadily decrease. This may seem unintuitive since one may assume that a higher mass transfer efficiency would lead to more massive compact objects and thus a more detectable population. However, this contributes to the envelope mass and so without increasing the core mass or fallback rate, the final compact object mass is relatively unaffected. Moreover, one must consider that most of these DCOs are formed through a common-envelope event and so retaining more of the envelope during mass transfer means that the eventual ejection of the envelope is much more difficult, thus leading to more stellar mergers and fewer detectable systems \citep[e.g.][]{Kruckow+2018,Broekgaarden+2021}.

@@

In model \modNoBH{} we do not give black holes natal kicks. For BHBHs, the rate is approximately equal to that of model \modSigLower{} since kicks of $30 \unit{km}{s^{-1}}$ are equivalent to no kicks for massive BHs in our sample. For BHNSs, this model's rate is still well above the fiducial but decreases slightly relative to model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick. NSNSs are unaffected as one would assume.

@@

In Figure~\ref{fig:lower_mass_gap_variation}, we show the component mass distribution for all LISA detectable DCOs (BHBHs, BHNSs and NSNSs) for two different remnant mass prescriptions. The grey distribution uses the Fryer \textit{delayed} remnant mass prescription \citep{Fryer+2012}, which is our fiducial assumption. This prescription produces compact objects in the lower mass gap ($2.5 \unit{M_{\odot}} \le m \le 5 \unit{M_{\odot}}$) and indeed we find that, of the LISA detectable DCOs, approximately \BHBHatLeastOneLowerMassGapPerc{}\% of BHBHs, \BHNSatLeastOneLowerMassGapPerc{}\% of BHNSs and \NSNSatLeastOneLowerMassGapPerc{}\% of NSNSs have at least one component in the lower mass gap. Overall, weighting by the relative detection rates, this gives that 55\% of our predicted LISA DCO detections  would have at least one component in the lower mass gap when using this remnant mass prescription.

@@

In Figure~\ref{fig:ecc_low_kick_variation}, we investigate how decreasing the magnitude of natal kicks from core-collapse supernovae affects the eccentricity distribution of LISA detectable DCOs. For reference, we show the mean fiducial distributions (model \modFid{}) as dashed lines (see lower left panel of Fig.~\ref{fig:fiducial_pdf_distributions} for full comparison). In the main curves, we reduce the velocity dispersion for core-collapse supernovae from $265 \unit{km}{s^{-1}}$ to $30 \unit{km}{s^{-1}}$ (model \modSigLower{}).

>>>>

In models \modBetaLow{}-\modBetaHigh{}, we set the mass transfer efficiency $\beta$ to a fixed value. For the BHBHs and BHNSs, as we increase $\beta$ the detection rates steadily decrease. This may seem unintuitive since one might assume that a higher mass transfer efficiency would lead to more massive compact objects and thus a more detectable population. However, this increase contributes to the envelope mass and so without increasing the core mass or fallback rate, the final compact object mass is relatively unaffected. Moreover, one must consider that most of these DCOs are formed through a common-envelope event and so retaining more of the envelope during mass transfer means that the eventual ejection of the envelope is much more difficult, thus leading to more stellar mergers and fewer detectable systems \citep[e.g.][]{Kruckow+2018,Broekgaarden+2021}.

@@

In model \modNoBH{} we do not give black holes natal kicks. For BHBHs, the rate is approximately equal to that of model \modSigLower{} since kicks of $30 \unit{km}{s^{-1}}$ are equivalent to no kicks for massive BHs in our sample. For BHNSs, this model's rate is still well above the fiducial but decreases slightly relative to model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick. NSNSs are unaffected as one would assume due to the absence of BHs.

@@

In Figure~\ref{fig:lower_mass_gap_variation}, we show the component mass distribution for all LISA detectable DCOs (BHBHs, BHNSs and NSNSs) for two different remnant mass prescriptions. The grey distribution uses the Fryer \textit{delayed} remnant mass prescription \citep{Fryer+2012}, which is our fiducial assumption (model \modFid{}). This prescription produces compact objects in the lower mass gap ($2.5 \unit{M_{\odot}} \le m \le 5 \unit{M_{\odot}}$) and indeed we find that, of the LISA detectable DCOs, approximately \BHBHatLeastOneLowerMassGapPerc{}\% of BHBHs, \BHNSatLeastOneLowerMassGapPerc{}\% of BHNSs and \NSNSatLeastOneLowerMassGapPerc{}\% of NSNSs have at least one component in the lower mass gap. Overall, weighting by the relative detection rates, this gives that 55\% of our predicted LISA DCO detections would have at least one component in the lower mass gap when using this remnant mass prescription.

@@

In Figure~\ref{fig:ecc_low_kick_variation}, we investigate how decreasing the magnitude of natal kicks from core-collapse supernovae affects the eccentricity distribution of LISA detectable DCOs. For reference, we show the mean fiducial distributions (model \modFid{}) as dashed lines (see Fig.~\ref{fig:fiducial_pdf_distributions}d for full comparison). In the main curves, we reduce the velocity dispersion for core-collapse supernovae from $265 \unit{km}{s^{-1}}$ to $30 \unit{km}{s^{-1}}$ (model \modSigLower{}).
